Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2016-10-29 apj.tex
fixing zeropoint

\documentclass{aastex61}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{lineno}
\usepackage{color}
\defcitealias{1999PASP..111...63F}{F99}
\linenumbers

@@

\subsection{Model}
We assume 
that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
on the
 equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
$EW_{Ca}$, $EW_{Si}$,
and $\lambda_{Si}$ the wavelength of the minimum of 
the SiII$\lambda6355$ feature:
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
The explicit omission of light-curve shape in our model is compensated by its proxy
$EW_{Si}$ at peak brightness
\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
$C_c$.  A grey magnitude offset, $\Delta$, is included for each supernova
to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
The observed magnitudes are linearly dependent on the
extrinsic-color parameters $k_0$ and $k_1$.  
The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
Unlike the parameters associated with
the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  the latent
parameters $k_0$ and $k_1$ are not directly associated
with observables but are rather drawn from the set of peak magnitudes.
The model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} \\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si}  \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} \\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} \\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si}
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$,  and $\eta$,  are the intercepts and slopes of the linear relationships that
relate intrinsic magnitudes with the spectral-feature parameters.
(In this article we freely interchange the parameter indices with  $01234$ and $UBVRI$.)
The global parameters $\gamma^0$, $\gamma^1$  are the slopes that connect the extrinsic-color
parameters to observed magnitudes.

@@

\color{red}
Recall that our model does not specify the color of a supernova that suffers no extrinsic effects, but rather sets the
mean of $k_0$ and $k_1$ of the distribution to zero.
There is an unconstrained $k_0^0$, $k_1^0$ that corresponds to an intrinsic supernova.  The true extinction is
$A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$ where $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$.
The true color excess is $E^T(B-V) = A^T_B-A^T_V$.
Despite this ambiguity, a linear slope relating the $E^T(B-V)$ and $A^T_V$ for a set of supernova is the same slope
relating $A_V$ and $E(B-V)$.
\color{black}
Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
which a linear fit gives a slope of $R_V=2.77^{+0.08}_{-0.09}$,
\color{red}
which is the observed broad-band total-to-selective extinction exhibited by our sample.
In contrast, the quantity $R^F_V = A^F_V/E^F(B-V)$ for an individual supernova is unspecified without knowledge of the intrinsic color.
For ta qualitative view, we choose $k_0$  and $k_1$ such that the bluest supernova roughly correspond to $E(B-V)=0$.
With this ansatz, we
estimate $R^T_V$ per supernova as shown in Figure~\ref{avebv:fig}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/avebv.pdf}
   \includegraphics[width=2.8in]{output11/rv.pdf}
   \caption{
	\color{red}
   Left: $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data. Right: Shown for qualitative purposes,
   $R^T_V=A^T_V/E^T(B-V)$ 
   versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova.  Overplotted is the mean and standard deviation of those points in equally divided bins.
   On both plots are overplotted the expected values for the \citetalias{1999PASP..111...63F} model
   for specific choices of $R^F_V$, normalized to have $A_V=0$ at $E(B-V)=0$.  Note that these lines are not straight on the left plot, and are not constant on the plot to the right.
   \color{black}
   \label{avebv:fig}}
\end{figure}

@@

\section{Supernova Model II: Two Extrinsic Parameters, One Intrinsic Parameter}
\label{model2:sec}
In \S\ref{model:sec} we show that the SNfactory data analyzed with an agnostic model with
two extrinsic parameters produce
magnitudes consistent
with two-parameter dust models that have been established for stars in the Milky Way, LMC, and SMC.
An extension to our model is now added to explore the possibility of
a possible additional
color parameter that could have its origins in supernova astrophysics.
The extended model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
In all aspects it is identical to the previous model except for the addition of the term $\delta D$,
which affects the mean
absolute magnitudes:
each supernova has an intrinsic $D$ parameter that is linearly related to
absolute magnitudes through global coefficients $\delta$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
its effects on broadband magnitudes.
Although
this term is introduced as part of the  absolute rather than observed magnitudes,
practically identical results are obtained when it is placed alongside the extrinsic $\gamma k$ terms.  Despite this
degeneracy, for convenience this term is referred to as ``intrinsic''.

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output15/ebv.pdf}
   \includegraphics[width=2.8in]{output15/ebv_delta.pdf}
      \caption{Left: Ideograms of the external $E(B-V)$ and
   internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess  for the supernovae in our sample.
   Right: Ideogram of $E_\delta(B-V)$ on an enlarged scale.
   \label{ebv:fig}}
\end{figure}
The significance of the $\delta$ parameters is shown pictorially.
Figure~\ref{deltacorner:fig} shows the $\delta$ posteriors, which are bimodal due to the $\pm$ sign degeneracy.  The probability
of the null result $\delta_X=0$ for all $X$ is $<98\%$, as determined through
the population of its bin in a 5-dimensional histogram.
Figure~\ref{deltaratio:fig} shows  values of $\delta_X/\delta_I-1$ that  have significant non-zero values.   An interesting feature
is that the shift in magnitude is not monotonic in wavelength, but rather decreases from $U$ to $V$, and then increases from $V$
to $I$.
These are not the behaviors expected from normal dust,
circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
2015ApJ...807L..26G} and so may be indicative of underlying supernova physics beyond that captured by $EW_{Ca}$, $EW_{Si}$ and
$\lambda_{Si}$.

@@

\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, and  
\citet{2015MNRAS.447.1247S} show that $v_{Si}$ is an important spectral classifier within the SNfactory data themselves.
The $\lambda_{Si}$ treated in this article varies linearly with $v_{Si}$.
The values of $\eta$ in this article are consistent with zero.  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color,
and in turn $\lambda_{Si}$ is correlated with $EW_{Ca}$.
Removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We conclude that $v_{Si}$ is correlated with color, 
but this correlation
is absorbed into the equivalent-width corrections, which give higher likelihood as they give lower residual dispersions $C_c$.

@@

\subsection{Improving SNe~Ia as Standard Candles}
The model and results presented here
carry information on the calibration of absolute magnitude.  The grey parameter $\Delta$ represents Hubble residuals after
application of the model, and its  $0.10$ mag dispersion has contributions from intrinsic dispersion, peculiar velocities, and
measurement uncertainties.  It is also subject to overtraining.
The  analysis of this article was intended to model the color behavior of supernovae in our dataset.
A new analysis insensitive to overtraining is required to robustly determine how
well this model can be used to measure supernova distances.

>>>>

\documentclass{aastex61}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{lineno}
\usepackage{color}
\defcitealias{1999PASP..111...63F}{F99}
\linenumbers

@@

\subsection{Model}
We assume 
that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
on the
 equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
$EW_{Ca}$, $EW_{Si}$,
and $\lambda_{Si}$ the wavelength of the minimum of 
the SiII$\lambda6355$ feature:
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
The explicit omission of light-curve shape in our model is compensated by its proxy
$EW_{Si}$ at peak brightness
\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
$C_c$.  A grey magnitude offset, $\Delta$, is included for each supernova
to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
The observed magnitudes are linearly dependent on the
extrinsic-color parameters $k_0$ and $k_1$.  
The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
Unlike the parameters associated with
the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  the latent
parameters $k_0$ and $k_1$ are not directly associated
with observables but are rather drawn from the set of peak magnitudes.
The model 
\color{red}
likelihood
\color{black}
is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} \\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si}  \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} \\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} \\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si}
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$,  and $\eta$,  are the intercepts and slopes of the linear relationships that
relate intrinsic magnitudes with the spectral-feature parameters.
(In this article we freely interchange the parameter indices with  $01234$ and $UBVRI$.)
The global parameters $\gamma^0$, $\gamma^1$  are the slopes that connect the extrinsic-color
parameters to observed magnitudes.

@@

\color{red}
Recall that our model does not specify the color of a supernova that suffers no extrinsic effects, but rather sets the
mean of $k_0$ and $k_1$ of the distribution to zero.
There is an unconstrained $k_0^0$, $k_1^0$ that corresponds to an intrinsic supernova.  The true extinction is
$A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$ where $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$.
The true color excess is $E^T(B-V) = A^T_B-A^T_V$.
Despite this ambiguity, a linear slope relating the $E^T(B-V)$ and $A^T_V$ for a set of supernova is the same slope
relating $A_V$ and $E(B-V)$.
\color{black}
Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
which a linear fit gives a slope of $R_V=2.77^{+0.08}_{-0.09}$.
\color{red}
The full set of supernovae does not coincide with the expectations of a single linear law; the supernova population rather appears to be peaked
on a ridge line, and having a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
but can have values that extend toward lower values.

The quantity $R^F_V = A^F_V/E^F(B-V)$ for an individual supernova is unspecified without knowledge of the intrinsic color.
For a qualitative view, we choose the zeros for $V$-band extinction and color-excess such that the bluest supernova roughly correspond to $E(B-V)=0$,
$A_V=0$, and such that the ridge line is close to flat.
With this ansatz, we
estimate $R^T_V$ per supernova as shown in Figure~\ref{avebv:fig}, with the expectations of the
 \citetalias{1999PASP..111...63F} model for fixed $R^F_V$ overplotted.
With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
\color{black}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/avebv.pdf}
   \includegraphics[width=2.8in]{output11/rv.pdf}
   \caption{
	\color{red}
   Left: $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data. Right: Shown for qualitative purposes,
   $R^T_V=A^T_V/E^T(B-V)$ 
   versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova. 
   %Overplotted is the mean and standard deviation of those points in equally divided bins.
   On both plots are overplotted the expected values for the \citetalias{1999PASP..111...63F} model
   for specific choices of $R^F_V$, normalized to have $A_V=0$ at $E(B-V)=0$.  Note that these lines are not straight on the left plot, and are not constant on the plot to the right.
   \color{black}
   \label{avebv:fig}}
\end{figure}

@@

\section{Supernova Model II: Two Extrinsic Parameters, One Intrinsic Parameter}
\label{model2:sec}
In \S\ref{model:sec} we show that the SNfactory data analyzed with an agnostic model with
two extrinsic parameters produce
magnitudes consistent
with two-parameter dust models that have been established for stars in the Milky Way, LMC, and SMC.
An extension to our model is now added to explore the possibility of
a possible additional
color parameter that could have its origins in supernova astrophysics.
The extended model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
In all aspects it is identical to the previous model except for the addition of the term $\delta D$,
which affects the mean
absolute magnitudes:
each supernova has an intrinsic $D$ parameter that is linearly related to
absolute magnitudes through global coefficients $\delta$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
its effects on broadband magnitudes.

\color{red}
The $\delta D$ terms contribute to the mean of the Normal distribution in Eqn.~\ref{ewsiv:eqn}, together with the spectral-feature terms:
it is for this reason that for convenience these terms are referred to as ``intrinsic''.
However, we emphasize now that we have also run the alternative case  of placing the
$\delta D$ terms in mean of the Normal distribution in Eqn.~\ref{dust:eqn}, i.e.\ as extrinsic contributions.
Analyses of the two different models give practically identical results, meaning that data are not constraining enough
to identify $\delta D$ as being physically intrinsic or extrinsic.
\color{black}

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output15/ebv.pdf}
   \includegraphics[width=2.8in]{output15/ebv_delta.pdf}
      \caption{Left: Ideograms of the external $E(B-V)$ and
   internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess  for the supernovae in our sample.
   Right: Ideogram of $E_\delta(B-V)$ on an enlarged scale.
   \label{ebv:fig}}
\end{figure}
The significance of the $\delta$ parameters is shown pictorially.
Figure~\ref{deltacorner:fig} shows the $\delta$ posteriors, which are bimodal due to the $\pm$ sign degeneracy.
\color{red}
Recall that fixing $\delta_X=0$ reverts this model into the two external-parameter model of \S\ref{model:sec}.
\color{black}
The probability
of the null result $\delta_X=0$ for all $X$ is $<98\%$, as determined through
the population of its bin in a 5-dimensional histogram.
Figure~\ref{deltaratio:fig} shows  values of $\delta_X/\delta_I-1$ that  have significant non-zero values. 
\color{red}
While the signal of the internal parameter is strong within the context of this model, ``model testing'' (comparing the
performance  between this model
and that of \S\ref{model:sec}), is challenging for Bayesian Monte Carlo analysis.  Evidence calculations are planned
for the next generation of STAN and the development of robust algorithms is a subject of theoretical work.
\color{black}

An interesting feature
is that the shift in magnitude is not monotonic in wavelength, but rather decreases from $U$ to $V$, and then increases from $V$
to $I$.
These are not the behaviors expected from normal dust,
circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
2015ApJ...807L..26G} and so may be indicative of underlying supernova physics beyond that captured by $EW_{Ca}$, $EW_{Si}$ and
$\lambda_{Si}$.

@@

\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, and  
\citet{2015MNRAS.447.1247S} show that $v_{Si}$ is an important spectral classifier within the SNfactory data themselves.
The $\lambda_{Si}$ treated in this article varies linearly with $v_{Si}$.
The values of $\eta$ in this article are consistent with zero.  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color,
and in turn $\lambda_{Si}$ is correlated with $EW_{Ca}$.
Removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
non-zero $\eta$ values at  $\gtrsim 2\sigma$.
\color{red}
The Ca and Si responsible for the equivalent widths and wavelength of our selected spectral features
are expected to be produced together in the thermonuclear burning into intermediate mass elements.
\color{black}
We conclude that $v_{Si}$ is correlated with color, 
but this correlation
is absorbed into the equivalent-width corrections, which give higher likelihood as they give lower residual dispersions $C_c$.

@@

\subsection{Improving SNe~Ia as Standard Candles}
The model and results presented here
carry information on the calibration of absolute magnitude.  The grey parameter $\Delta$ represents Hubble residuals after
application of the model, and its  $0.10$ mag dispersion has contributions from intrinsic dispersion, peculiar velocities, and
measurement uncertainties.
\color{red}
The purpose of this analysis was designed to mine information from the SNfactory data set, and so the results presented here
are specific to it both in terms of its population distribution and potentially noise.  This is the approach taken by previous
exploratory work.
A new analysis that explicitly measures out-of-sample performance is required to robustly determine how
well the addition of third parameter inferred from supernova magnitudes can be used to measure supernova distances.
\color{black}
